---
title: "Movies and TV Shows on Various Streaming Platforms"
author: "Hannah Burrows, Sabrina Fang, Christian Tsao, and Ryu Ngammuang"
date: "11/30/2020"
output: html_document
---


```{r setup, include=FALSE, warning=FALSE}

source("scripts/summary_table.R")
source("scripts/summary_info.R")
source("scripts/chart_1.R")
source("scripts/chart_2.R")
source("scripts/chart_3.R")
# other sources go here

amazon_data <- read.csv("data/amazon_prime_tv_shows.csv",
  stringsAsFactors = FALSE
)
disney_data <- read.csv("data/disney_plus_shows.csv",
  stringsAsFactors = FALSE
)
netflix_data <- read.csv("data/netflix_movies_and_tv.csv",
  stringsAsFactors = FALSE
)
netflix_2_data <- read.csv("data/netflix_movies_and_tv_imdb_ratings.csv",
  stringsAsFactors = FALSE
)

knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
With the COVID-19 pandemic forcing many people to stay home, many have turned
towards means of entertainment that don’t require going outside or interacting
with others, such as using streaming services like Amazon Prime Video, Disney+,
and Netflix to watch movies and TV shows. Analyzing how these streaming
platforms and their users may have changed during the pandemic may provide
insight into how we have adjusted to life in isolation. Additionally, this
analysis may reveal insights into how streaming services have improved and
adjusted overtime to increase subscriptions and revenue, how demographics of
different streaming services vary and have changed over time, and how the
popularity of different genres compare within each streaming service and
compared to other streaming services. 

To answer these questions, this report uses data collected by various kaggle
users about movies and TV shows on three popular streaming services –--
[Amazon Prime Video](https://www.kaggle.com/nilimajauhari/amazon-prime-tv-shows),
[Disney+](https://www.kaggle.com/unanimad/disney-plus-shows), and
[Netflix](https://www.kaggle.com/shivamb/netflix-shows) (which has a [second source](https://www.kaggle.com/sarahjeeeze/imdbfile). 


## Summary
One value that could be useful to look at is the average IMDb ratings for all the movies in the dataset. For Amazon Prime, that rating is `r summ_info$ama_avg_rating`, while Netflix's average rating is `r summ_info$net_avg_rating`. Looking at the average IMDb values for a streaming service allows us to see how well received the average show on that streaming service is, and we can compare how well the average shows from each streaming service does. Here we can see that Amazon Prime's shows scores, on average, about 1 point higher than Netflix's. 
  
Other values that could be useful is the oldest show that a streaming service has to offer, and what that =show is called. On Amazon Prime, the oldest show is `r summ_info$ama_old_title`, which released on `r summ_info$ama_old_year`, while Netflix's oldest show is `r summ_info$net_old_title`, which released on `r summ_info$net_old_year`. Looking at the oldest show on a streaming service can let us see how dedicated a streaming service is, because older shows tend to have lower view counts (due to the fewer amount of "new watchers"). Here we can see that Netflix's oldest show is just 1 year older than Amazon Prime's oldest show.


## Aggregate Table
The table created displays the year, the highest and lowest rating of that year,
the total number of movies that released in that year, the most common language used,
the most common rating and the most common genre between all movies released that year.
The data was grouped by year to show summarized information for each year.
Below is an example of the summarized data for Disney prime movies and TV shows.

```{r aggregate table, echo = FALSE,message = FALSE, warning = FALSE}
library("knitr")
library("kableExtra")
kable(
  summary_table(disney_data), align = "c",
  col.names = c("Year", "No. of Movies", "Highest rating", "Lowest rating", "Most common language", "Most common rating", "Most common genre")
  ) %>%
  kable_styling(font_size = 15) %>%
  kable_styling(latex_options = "scale_down") %>%
  column_spec(3, color = 'green') %>%
  column_spec(4, color = 'red')
```

From the table, we can tell one key insight about Disney prime shows is that in the past few years, the general rating of shows produced are 'PG-13', and we can also see that English is the primary language used in the movies produced throughout all the years. We can also see a trend that shows released in the early 1900s were generally rated 'G', and later the ratings for shows started to become 'PG', and then in the 2000s, shows became generally rated 'PG-13'.
As we observe the genres, we can also see that 'Adventure' and 'Comedy' are the 2 most common genres throughout the history of Disney prime shows.

## Charts
3 charts display information from the data (what you visualize is up to you).
Describe the purpose of each chart (e.g., "this chart was intended to show the 
relationship between..."), render each chart, and describe pertinent 
observations found in each chart

### Chart 1 - Popularity of Genres for TV Shows
```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.dim=c(10, 6)}
chart_1(netflix_data, disney_data, amazon_data)
```

This chart was intended to show the popularity of various genres of TV Shows on 
each of the streaming services, in order to analyze if there was a particular
streaming service that was preferred for specific genres.(Note: this was done
by comparing the percent of total shows on each platform for each genre; for
ease of viewing, only the top 5 genres from each platform are shown, and so
percents may not total to 100).

This chart reveals that there are definitely most popular genres for each
platform, and that they vary between platforms. For example, the most popular
genre on Disney+, by far, is Animation, at 52.41% of its total TV streaming
library, while the most popular on Amazon Prime Video is Drama at 51.15%, and
the most popular on Netflix is International at 39.61%. While there are
definitely potential questions in how these shows' genres were defined (what
exactly constitutes a "Drama", for example?), this does reveal some interesting
insights into the popularity of various genres on these streaming services, as
well as potentially how these platforms have optimized to increase their
subscriptions and revenue. For example, there is very little overlap in the
most popular genres on each platform (Comedy, Documentary, Kids, and Action are
the only overlapping genres between the platforms, and not one of them made it
into the top 5 in all 3 platforms). In addition, the most popular genre on each
platform didn't make it to the top 5 most popular genres for either of the other
platforms. While this could be a coincidence, this could also be an intentional
action on behalf of the streaming platforms to increase subscriptions and
maximize revenue by seeking to fill a niche/provide primarily content users
would be unable to find on other platforms, thus increasing the chances that the
average person subscribes to all three platforms instead of just one and therein
maximizing the profit of all three companies.

### Chart 2 - Age Demographic of Content in Streaming Services
```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.dim=c(10, 6)}
ratings_plot(amazon_data, disney_data, netflix_data)
```

This chart was intended to show the amount of content for each age group from each year on all of the streaming services combined to identify trends in content for each age group and how the pandemic might have altered content production. This was done by comparing the # of Shows or Movies produced each year for each age group. Note that the age groups are classified by the Motion Picture Association film rating system.

This chart reveals a content growth trend for each age group, and that content grows at a different rate for each age group. For example, approaching 2018, the amount of content rated R seemed to increase at an exponential rate, while the content growth rate of NC-17 material seemed to remain static. However, most age groups experienced a content decline in 2019, and an even steeper decline in 2020. In addition, most age groups had the max amount of content production in 2018, which indicates that streaming services were heavily saturated with new content in 2018. Though the growth rate of content per age group is different, production often increases and decreases at the same time for all age groups. The overall decline in 2020 is likely correlated with the pandemic, as the economy and and production process has been slowed. Even though the data is not complete (because 2020 is not over), it is unlikely that enough content will be produced in any age group to surpass growth rates leading up to 2018. Although the exponential increase of rated R material can not be explained by this chart, it suggests that interest in rated R content has increased, resulting in a wider audience and more revenue.

### Chart 3 - IMDB Movie Ratings of Movie Runtimes
```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.dim=c(10, 6)}
imdb_ratings_plot(disney_data, netflix_2_data)
```

This chart was intended to organize the IMDB ratings of movies from two streaming services based on their runtime to find how movie runtime correlates with IMDB rating and also identify the most popular movie rating and runtime on each streaming service. This was done by comparing IMDB ratings to runtimes to locate runtimes and ratings with a high (or low) concentration of movies. Note that that runtime is the total duration of a film, so TV Shows can not be included in this chart.

This chart reveals movie runtimes and IMDB ratings which have the highest concentration of movies from Netflix and Disney+. For example, the highest concentration of movies from Netflix exists where the IMDB rating is 7. In contrast, the highest concentration of movies from Disney+ exists where the IMDB rating is 6.5. In addition, Netflix has multiple films with a rating of 0, while Disney+ has a group of films with runtimes between 0 and 15 minutes. Most movies in both streaming services have a rating greater than 3 or less than 9, indicating that movies from Netflix and Disney+ deviate from their average IMDB rating a similar amount. Netflix has more movies and a higher average IMDB rating than Disney+, which likely accounts for part of its large subscriber base. Thus, this chart illustrates how Netflix motivates its subscriber base with a larger amount of films because its average IMDB rating is not significantly higher than the average rating for Disney+. The highest rated movie on Netflix is 66 minutes while the highest rated movie on Disney+ is 124 minutes, which suggests that Disney+ contains longer films which attract wider audiences while Netflix contains shorts films which attract wider audiences.
