---
title: "Movies and TV Shows on Various Streaming Platforms"
author: "Hannah Burrows, Sabrina Fang, Christian Tsao, and Ryu Ngammuang"
date: "11/30/2020"
output: html_document
---


```{r setup, include=FALSE}

source("scripts/chart_1.R")
source("scripts/chart_2.R")
#other sources go here

amazon_data <- read.csv("data/amazon_prime_tv_shows.csv", stringsAsFactors = FALSE)
disney_data <- read.csv("data/disney_plus_shows.csv", stringsAsFactors = FALSE)
netflix_data <- read.csv("data/netflix_movies_and_tv.csv", stringsAsFactors = FALSE)

knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
With the COVID-19 pandemic forcing many people to stay home, many have turned
towards means of entertainment that don’t require going outside or interacting
with others, such as using streaming services like Amazon Prime Video, Disney+,
and Netflix to watch movies and TV shows. Analyzing how these streaming
platforms and their users may have changed during the pandemic may provide
insight into how we have adjusted to life in isolation. Additionally, this
analysis may reveal insights into how streaming services have improved and
adjusted overtime to increase subscriptions and revenue, how demographics of
different streaming services vary and have changed over time, and how the
popularity of different genres compare within each streaming service and
compared to other streaming services. 

To answer these questions, this report uses data collected by various kaggle
users about movies and TV shows on three popular streaming services –--
[Amazon Prime Video](https://www.kaggle.com/nilimajauhari/amazon-prime-tv-shows),
[Disney+](https://www.kaggle.com/unanimad/disney-plus-shows), and
[Netflix](https://www.kaggle.com/shivamb/netflix-shows). 


## Summary
summary paragraph that includes information calculated by your summary
information function


## Table
A table of  aggregated data (e.g., that has been "grouped" by one of your
features); Render your table and describe pertinent observations found in it


## Charts
3 charts display information from the data (what you visualize is up to you).
Describe the purpose of each chart (e.g., "this chart was intended to show the 
relationship between..."), render each chart, and describe pertinent 
observations found in each chart

### Chart 1 - Popularity of Genres for TV Shows
```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.dim=c(10, 6)}
chart_1(netflix_data, disney_data, amazon_data)
```

This chart was intended to show the popularity of various genres of TV Shows on 
each of the streaming services, in order to analyze if there was a particular
streaming service that was preferred for specific genres.(Note: this was done
by comparing the percent of total shows on each platform for each genre; for
ease of viewing, only the top 5 genres from each platform are shown, and so
percents may not total to 100).

This chart reveals that there are definitely most popular genres for each
platform, and that they vary between platforms. For example, the most popular
genre on Disney+, by far, is Animation, at 52.41% of its total TV streaming
library, while the most popular on Amazon Prime Video is Drama at 51.15%, and
the most popular on Netflix is International at 39.61%. While there are
definitely potential questions in how these shows' genres were defined (what
exactly constitutes a "Drama", for example?), this does reveal some interesting
insights into the popularity of various genres on these streaming services, as
well as potentially how these platforms have optimized to increase their
subscriptions and revenue. For example, there is very little overlap in the
most popular genres on each platform (Comedy, Documentary, Kids, and Action are
the only overlapping genres between the platforms, and not one of them made it
into the top 5 in all 3 platforms). In addition, the most popular genre on each
platform didn't make it to the top 5 most popular genres for either of the other
platforms. While this could be a coincidence, this could also be an intentional
action on behalf of the streaming platforms to increase subscriptions and
maximize revenue by seeking to fill a niche/provide primarily content users
would be unable to find on other platforms, thus increasing the chances that the
average person subscribes to all three platforms instead of just one and therein
maximizing the profit of all three companies.

### Chart 2


### Chart 3
