---
title: "Movies and TV Shows on Various Streaming Platforms"
author: "Hannah Burrows, Sabrina Fang, Christian Tsao, and Ryu Ngammuang"
date: "11/30/2020"
output: html_document
---


```{r setup, include=FALSE}

source("scripts/chart_1.R")
source("scripts/chart_2.R")
#other sources go here

amazon_data <- read.csv("data/amazon_prime_tv_shows.csv", stringsAsFactors = FALSE)
disney_data <- read.csv("data/disney_plus_shows.csv", stringsAsFactors = FALSE)
netflix_data <- read.csv("data/netflix_movies_and_tv.csv", stringsAsFactors = FALSE)

knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
With the COVID-19 pandemic forcing many people to stay home, many have turned towards means of entertainment that don’t require going outside or interacting with others, such as using streaming services like Amazon Prime Video, Disney+, and Netflix to watch movies and TV shows. Analyzing how these streaming platforms and their users may have changed during the pandemic may provide insight into how we have adjusted to life in isolation. Additionally, this analysis may reveal insights into how streaming services have improved and adjusted overtime to increase subscriptions and revenue, how demographics of different streaming services vary and have changed over time, and how the popularity of different genres compare within each streaming service and compared to other streaming services. 

To answer these questions, this report uses data collected by various kaggle users about movies and TV shows on three popular streaming services – **Amazon Prime Video**, **Disney+**, and **Netflix**. 


## Summary
summary paragraph that includes information calculated by your summary
information function


## Table
A table of  aggregated data (e.g., that has been "grouped" by one of your
features); Render your table and describe pertinent observations found in it


## Charts
3 charts display information from the data (what you visualize is up to you).
Describe the purpose of each chart (e.g., "this chart was intended to show the 
relationship between..."), render each chart, and describe pertinent 
observations found in each chart

### Chart 1 - Popularity of Genres for TV Shows
```{r, echo = FALSE, warning=FALSE, message=FALSE}
chart_1(netflix_data, disney_data, amazon_data)
```

This chart was intended to show the popularity of various genres of TV Shows on 
each of the streaming services, in order to analyze if there was a particular
streaming service that was preferred for specific genres.
This chart reveals that ___

### Chart 2


### Chart 3
