---
title: "Movies and TV Shows on Various Streaming Platforms"
author: "Hannah Burrows, Sabrina Fang, Christian Tsao, and Ryu Ngammuang"
date: "11/30/2020"
output: html_document
---


```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)

source("scripts/chart_1.R")
#other sources go here

amazon_data <- read.csv("data/amazon_prime_tv_shows.csv", stringsAsFactors = FALSE)
disney_data <- read.csv("data/disney_plus_shows.csv", stringsAsFactors = FALSE)
netflix_data <- read.csv("data/netflix_movies_and_tv.csv", stringsAsFactors = FALSE)
#netflix_subscriber_data <- read.csv("data/NetflixSubscribersbyCountryfrom2018toQ2_2020", stringsAsFactors = FALSE)
#for some reason I can't get this to load correctly - if you can see what I'm
#doing wrong, please feel free to fix it! 

knitr::opts_chunk$set(echo = TRUE)
```

## Introduction



## Summary
summary paragraph that includes information calculated by your summary
information function


## Table
A table of  aggregated data (e.g., that has been "grouped" by one of your
features); Render your table and describe pertinent observations found in it


## Charts
3 charts display information from the data (what you visualize is up to you).
Describe the purpose of each chart (e.g., "this chart was intended to show the 
relationship between..."), render each chart, and describe pertinent 
observations found in each chart

### Chart 1 - Popularity of Genres for TV Shows
```{r, echo = FALSE}
chart_1(netflix_data, disney_data, amazon_data)
```
This chart was intended to show the popularity of various genres of TV Shows on 
each of the streaming services, in order to analyze if there was a particular
streaming service that was preferred for specific genres.
This chart reveals that ___

### Chart 2


### Chart 3
